### 2017-06-06 paper/sexSelectionSpacing-ver1.tex
Try to fix Makefile
- dependencies do not appear to work
- .eps does not work with pdflatex :-(
Move to XeLaTeX for paper
- download TeX Gyre Pagella
- change preamle to tex document to allow for both text and math
- update ReadMe with download location for fonts
- update ReadMe with instructions to use XeLaTeX

\usepackage{mathpazo}
\usepackage[title]{appendix}
\usepackage[margin=1.0in]{geometry}
\usepackage[figuresleft]{rotating}
\usepackage[longnamesfirst]{natbib}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{dcolumn}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage[flushleft]{threeparttable}
\usepackage{setspace}
\usepackage{xyling}
\usepackage[justification=centering]{caption}
\usepackage[font=scriptsize]{subfig}
\usepackage[pdftex,colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black]{hyperref}
\usepackage{adjustbox}
\usepackage{xfrac}

@@

\begin{document}
\graphicspath{{figures/}}
\DeclareGraphicsExtensions{.jpg,.pdf,.mps,.png}

@@

% \setcounter{page}{0}
\newpage

\doublespacing
% \onehalfspacing

% \thispagestyle{empty}

\maketitle
\thispagestyle{empty}

\newpage
\doublespacing

@@

Son preference can manifest itself through other channels than sex selection.
Differential investments in education and health across boys and girls, resulting in
lower education and higher mortality of girls relatively to boys, could be thought 
of as evidence of son preference, although \cite{rosenzweig82} argue that both may 
represent parents' rational response to market opportunities rather than inherent 
preferences of parents.
Whatever way son preference presents itself, it appears that the dominant  
preference---as expressed through use of sex selection---is for one son, rather 
than multiple sons.

>>>>

\usepackage{fontspec}
\setromanfont[Ligatures=TeX]{TeX Gyre Pagella}
\usepackage{unicode-math}
\setmathfont{TeX Gyre Pagella Math}
% \usepackage{mathpazo}
\usepackage[title]{appendix}
\usepackage[margin=1.0in]{geometry}
\usepackage[figuresleft]{rotating}
\usepackage[longnamesfirst]{natbib}
\usepackage{dcolumn}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage[flushleft]{threeparttable}
\usepackage{setspace}
\usepackage{xyling}
\usepackage[justification=centering]{caption}
\usepackage[font=scriptsize]{subfig}
\usepackage[xetex,colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black]{hyperref}
\usepackage{adjustbox}
\usepackage{xfrac}

@@

\begin{document}
\graphicspath{{../figures/}}
\DeclareGraphicsExtensions{.eps,.jpg,.pdf,.mps,.png}

@@

% \setcounter{page}{0}

\newpage
\thispagestyle{empty}
\doublespacing

@@

Son preference can manifest itself through other channels than sex selection.
Differential investments in education and health across boys and girls, resulting in
lower education and higher mortality of girls relatively to boys, could be thought 
of as evidence of son preference, although \cite{rosenzweig1982a} argue that both may 
represent parents' rational response to market opportunities rather than inherent 
preferences of parents.
Whatever way son preference presents itself, it appears that the dominant  
preference---as expressed through use of sex selection---is for one son, rather 
than multiple sons.

\begin{figure}[htp]%
\centering
\includegraphics[width=0.9\textwidth]{spell2_g3_high_r4_s.eps}
\caption{Survival curve example}
\label{fig:survival}
\end{figure}
